\textbf{Case Studies II - Community Talks}

### 2013-04-22 ricardogarfe/final_report/007-libre-desktop-laws-community-talk.tex
Update ricardogarfe

\subsection{Ministerio de Administraciones Públicas}

\par Miguel Angel Amutio Chief of Planning and Operations area at \textit{Ministerio de Administraciones Públicas}made a study to introduce FLOSS advantages inside CCAA project development in 2005. This translation from FLOSS to human-readable content is necesary to spread FLOSS advantages inside a new area.

>>>>

\subsection{Ministerio de Administraciones P\'ublicas}

\par Miguel Angel Amutio Chief of Planning and Operations area at \textit{Ministerio de Administraciones P\'ublicas} made a study to introduce FLOSS advantages inside CCAA project development in 2005. This translation from FLOSS to human-readable content is necesary to spread FLOSS advantages inside a new area.
